Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful

### 2015-03-03 tuningpredictor.tex
safety commit

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fu, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

\maketitle
\begin{abstract}
Data mining techniques have been widely applied to software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning process will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

@@

How ``true'' are the  models generated by software analytics?
Suppose we use a model generated from software project data to, for example,
assess the relative value of OO metrics vs procedural metrics for predicting
project defects. Are we reporting ``truth'' in any sense of the word? And for home
many other projects might we find that same ``truth''?

@@

Classification is an important approach to predict whether some modules in the projects are 
defective or non-defective. The general idea is to train the learners by using parts of data 
sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
based an different data mining classifiers, including CART, Random Forest 
\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
defective learner outperformed others according to their experiment and statistical analysis. 
To evalute those learners objectively in terms of accuracy, Lessmann et al
\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
significantly in terms of the area under the receiver operating characteristics curve(AUC). 
Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
those CART's parameters by search-based software engineering method can improve the 
performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
consider other possible parameters in CART which would have impact on the structure of 
trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.

@@

@@

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\cline{1-5}
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

@@

%%%%parameters for pd %%%%%%
\begin{figure*}[!ht]
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

>>>>

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Implications of Differential Evolution for  Defect Prediction:
Analytics Without Parameter Tuning Considered Harmful}
\numberofauthors{1}
\author{
\alignauthor
Wei Fu, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

\maketitle
\begin{abstract}

software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning process will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

@@

How ``true'' are the  models generated by software analytics?
Suppose we use a model generated from software project data to, for example,
assess the relative value of OO metrics vs procedural metrics for predicting
project defects. Are we reporting ``truth'' in any sense of the word? And for how
many other projects  and how many kinds of questions might we find that same ``truth''?

This is not some abstract question-- it is an open and pressing matter.
Any reading of the recent proceedings of FSE, ICSE, ASE, etc will discover hundreds
of papers using data miners to make conclusions about software projects. 
For example, some  analysts have made conclusions
about 
{\em what attributes
have most influence on a software project}.
For example, in 2013,
Rahman et al
\cite{rahman2013how}  used results from logistic regression to conclude
that code metrics are generally less useful than process
metrics for  predicting defects from static code analysis.  
In the same year, Bell et al. (who also used negative binomial regression) argued that
software defect prediction was not improved by adding in~\cite{bell2013limited}.

@article{bell2013limited,
  title={The limited impact of individual developer data on software defect prediction},
  author={Bell, Robert M and Ostrand, Thomas J and Weyuker, Elaine J},
  journal={Empirical Software Engineering},
  volume={18},
  number={3},
  pages={478--505},
  year={2013},
  publisher={Springer}
}

The results of this paper offer a very different picture  to recent prominent results from prior authors.
Lessmann et al.~\cite{lessmann2008benchmarking}, Rahman et al.~\cite{rahman2013how} and Arshiholm et al.~\cite{arisholm06} argue that when it comes to defect prediction, different learners often
produce statistically similar results. For this reason  Rahman et al. only present results their logistic
regression results, commenting that ``dor brevity, only results from LR are
presented; other learning models give similar results''~\cite{rahman2013how}. Note that those prior results,
where most learners achieved the same results, arose from the default parameter settings from those learners.

Our results, on the other hand, come from tuning a data miner's parameters. In those results,
we found that the choice of parameters had dramatic impacts on data mining performance.
For example, we show results below where:   
\bi 
\item 
Tuning improved precision values from  2\% to 98\%; or
\item 
Tuning improved false alarm values from 69\% to 0\%; or
\item 
Tuning improved recall values from 0 to 100\%; or
\item 
Tuning improved the f-measure (which is the harmonic mean of recall and precision) from 0 to 86\%.
\ei   
In terms of changing SE research methodologies, an important aspect of these results is that usually XXXX always different. cannot determine without experimentation which learner will, after tuning, yield the best results for a particular data set. Hence it is no longer viable for researchers to trust the recommendations 
of other researchers working with other data sets that ``data miner XYZ is best''. Before
offering a conclusion about a particular data set, researchers need now augment  their 
papers with preliminary tuning studies (the results of which select the tunings+data miners to be used
to make conclusions for the second half of their paper).

The good news is that such tuning is not an arduous task. The differential evolution algorithm 
used in this study is wdiely available in many standard  toolkits and languages\footnote{See the long list at
www1.icsi.berkeley.edu/~storn/code.html.}
And even if somehow those tools and prior implementations are not workable at a local site, 
differential evolution is very simple to code. Hence, it can readily and quickly implemented.

When we discuss these results with colleagues, one response we get is ``enough of the parameter tuning.. lets use simpler methods''. 
While we understand their motivation (to keep thing simple), software project
data cannot necessarily be condensed to (say) a simple univariate analysis that
reports how one independent variable effects a dependent variable.
Such a simplistic analysis can miss significant interaction
effects when multiple factors combine to effect the target variable. For example,
one of the base results in defect prediction is that predictors formed from
a single variable perform much worse than those can combined multiple variables (three or more)~\cite{me07b}.

If those results come from an analysis of a complex interactions between attributes,
then some kind of data mining method\footnote{By this term we mean the
full gamut of methods for large-scale analysis of
data including statistical
parametric methods (that assume a particular distribution then strive to learn the parameters of that distribution); kernel methods;
dimensionality  synthesis methods; 
instance weighting schemes; feature subset selection methods
outlier removal methods;
decision tree learners; neural networks; and instance-based
methods including clustering and/or   case-based reasoning.} then there is the
{\em tuning problem} of how to set the myriad of parameters that 
control the learner.

\item
What data miners are better than others for particular tasks
in software analytics. 
\ei

Also, in 2007, one of us (Menzies) claimed that Naive Bayes
classifiers with a certain lind of pre-processor were better than entropy-based decision trees for defect prediction~\cite{me07b}.
Similarly, in 2008 Lessmann et al.~\cite{lessmann2008benchmarking} argued  that 
Random Forests~\cite{brieman00} and CART ~\cite{brieman84} work best, worst for learning software defect predictors from
static code attributes. Similar claims that one learner was better than another
have been made by many other authors; e.g.

We write to suggest that all those conclusions may be wrong or, at the very most,
correct within a very limited context. At the very least, the conclusions
of those papers (and literally dozens of similar papers, include severl
of our own~\cite{me02e,me02k,me03a,me06d,me07b}) need to be revisited
in light of this paper's results on the effects of tuning on data miners.

Machine learners
are controlled by parameters that decide (e.g.) when to stop recursively
dividing data into smaller section or (e.g.) what thresholds for errors are small
enough to be acceptable. When used ``off-the-shelf'', analytst
use default settings for those parameters. We find that  a 
simple optimization scheme (differential evolution) can find much
better tunings that can dramatically change the performance of
the learned model (measured in terms of false alarm rates, recall,
precision, f-measure, and g-measure).  From this first result,
we conclude that {\bf parameter tuning with some optimizer such as differential
evolution should become standard practice}.

Our next observation is that observations about miner1 being better
than miner2 do not survive tuning. To be specific: given some
ranking of data miners for some task such as defect prediction,
we find that tuning can reverse those rankings such that the worst untu

Tuning the data miners with different evolution takes some
times (around an order of magnitude slower than the learning), but not an impractically slower amount of time. Further, when we look at what
attrub

@@

Classification is an important approach to predict whether some modules in the projects are 
defective or non-defective. The general idea is to train the learners by using parts of data 
sets(e.g. ant 1.3, 1.4 in PROMISE\footnote{http://openscience.us/repo/}) and predict with 
remaining ones(ant 1.5, 1.6 and 1.7). Many types of defect predictors have been proposed 
based an different data mining classifiers, including CART, Random Forest 
\cite{guo2004robust},  Naive Bayes\cite{menzies2007data},Logistic Regression 
\cite{khoshgoftaar1999logistic}. During the past years, authors claimed that their new 
defective learner outperformed others according to their experiment and statistical analysis. 
To evalute those learners objectively in terms of accuracy, Lessmann et al
\cite{lessmann2008benchmarking} carried out a study to compare 22 classifiers over 10 public 
\begin{figure}
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
When applying case-based reasoning, researchers use different settings including how they measure dis- tance between instances (examples include the Euclidean measure, Manhattan and Chebyshev). Other settings control if numerics are normalized min..max to 0..1, before they are used in the distance measure.

Another set of settings refers to how to handle non-numeric distances or missing values. Some researchers delete training data with missing information while others compute missing values via, say, median values.

After feature selection comes instance selection. There are many settings for instance selectors such as use outlier removal or prototype generation. Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
The next set of settings concern how many neighbors to use (k=1,2,5,etc). Some researchers set “k” in dynamic pre-learning phase that checks the training data to find what “k” works best for that data.

Once the neighbors are known, the next settings control how to summarize their information. Some researchers use means, other use medians, or a weighted sum that uses the distance of the neighbor from the test instance (and that weighting might be determined by some kernel such as uniform, triangular, Gaussian, cosine, or Epanechnikov).
Researchers may use other settings to control different pre-processors. E.g. some discretize numeric values (via equal width or equal frequency) using some binning policy (and researchers differ on how many bins are best).\\\hline
\end{tabular}
\caption{Some tunings for SE predictive systems. Found by this author while preparing this proposal in a day of reading the SE predictive modeling literature on case-based reasoning and effort estimation. Note that other kinds of prediction systems (decision trees, neural nets, linear repression, etc) have yet more adjustable design options.}\label{fig:adjust}
\end{figure}

domain data sets from the NASA Metrics Data repository. By using Nemenyi's post hoc test 
with $\alpha = 0.05$, they concluded that the predictive accuracy of most learners didn't differ 
significantly in terms of the area under the receiver operating characteristics curve(AUC). 
Furthermore, according to the fig.2 in \cite{lessmann2008benchmarking}, Random Forest is 
significantly better than CART. Lessmann's paper motivates us to investigate whether tuning 
those CART's parameters by search-based software engineering method can improve the 
performance. Even though Lessmann considered unpruned tree and pruned tree, They didn't 
consider other possible parameters in CART which would have impact on the structure of 
trees, like the depth of the tree, the maximum and minimum number of leafs of the tree.

@@

\begin{figure}[!t]

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
  \begin{tabular}{r@{~}|r@{~}rr|r@{~}rr|r@{~}rr}
    & \multicolumn{3}{c|}{WHERE}&\multicolumn{3}{c|}{CART}& \multicolumn{3}{c}{Random Forest}\\\cline{2-10} 
    Goal & tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive &$\frac{\mathit{tuned}}{\mathit{naive}}$& tuned & naive&$\frac{\mathit{tuned}}{\mathit{naive}}$\\\hline
pd&242&13&19&7&1&9&13&1&10\\ 
prec&159&13&12&9&1&13&18&2&11\\
f&303&13&23&7&1&10&14&2&9 
  \end{tabular}
  \caption{For one train/test set pair (ANT),  time (in seconds) spent tuning,
  for different goals, or just running the ``off-the-shelf'' learner.}
\end{figure}

\begin{figure}[!t]

\renewcommand{\baselinestretch}{0.8}
\scriptsize
\centering
\begin{tabular}{r|rrr}
goal &	WHERE	&CART&	Random Forest\\\hline
f	&15	&13	&9\\ 
pd	&15	&16	&8\\ 
prec&	14	&14	&8
\end{tabular}
\caption{How much slower is tuning vs just running the default
settings of the learner? E.g. bottom right, tuning to increase
precision with Random Forests is eight times slower than
just running Random Forests.}
\end{figure}

@@

%%%%%%%%%%%%%%%% list of parameters%%%%%%%%%%%%%%%%%%%%%
\renewcommand\arraystretch{1.2}
\begin{figure*}[t!]
\renewcommand{\baselinestretch}{0.8}
\scriptsize
  \centering
	\begin{tabular}{|c|c|c|c|l|}
	\cline{1-5}
	\begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular} & Parameters & Default &\begin{tabular}[c]{@{}c@{}}Tuning\\ Range\end{tabular}& 
\multicolumn{1}{c|}{Description} \\ \hline
	\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where-based\\ Learner\end{tabular}} 
	& threshold & 0.5 &[0.01,1]& The value to determine defective or not .\\ \cline{2-5} 
	& infogain & 0.33 &[0.01,1]& The percentage of features to consider  for the best 
split to build CART tree\footnote{Since the Where-based learner will build two trees, the first 
one is for clustering and the second one is building prediction model. we explicitly call Where-
clustering tree and CART tree, respectively}. \\ \cline{2-5} 
	 & min\_sample\_size & 4& [1,10]& The minimum number of samples required to be a leaf for 
CART tree. \\ \cline{2-5} 
	 & min\_Size & 0.5 &[0.01,1]& \begin{tabular}[c]{@{}l@{}}The value to determine the minimum 
number of samples to be a Where-clustering tree \\ based on  ${n\_samples}^ {min\_Size}$.
\end{tabular} \\ \cline{2-5} 
    & wriggle & 0.2 &[0.01, 1] & The threshold to determine which branch in  Where tree to be pruned\\ \cline{2-5}
	 & depthMin & 2 & [1,6]&The minimum depth of the tree below which no pruning for Where-
clustering tree. \\ \cline{2-5} 
	 & depthMax & 10 &[1,20]& The maximum depth of the Where-clustering tree. \\ \cline{2-5} 
	 & wherePrune & False &T/F& Whether or not to prune the Where-clustering tree. \\ \cline{2-5}
	 & treePrune & True &T/F& Whether or not to prune the classification tree built by CART. \\ \cline{2-5} 
\hline
\multirow{4}{*}{CART} & threshold & 0.5 &[0,1]& The value to determine defective or not. \\ \cline{2-5} 
	 & max\_feature & None &[0.01,1]& The number of features to consider when looking for the best 
split. \\ \cline{2-5}

@@

%%%%parameters for pd %%%%%%
\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.8}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.17& 0.17& 0.02& 0.04& 0.42& 0.7& 0.8& 0.25& 0.32& 0.13& 0.61& 0.77& 0.09& 0.02& 0.68& 0.17& 0.01\\ \cline{2-20}
& infoPrune& 0.33& 0.13& 0.06& 0.12& 0.35& 0.44& 0.26& 0.33& 0.81& 0.03& 0.32& 0.89& 0.05& 0.1& 0.97& 0.15& 0.24& 0.01\\ \cline{2-20}
& min\_sample\_size& 4& 5& 2& 4& 1& 7& 6& 9& 6& 9& 8& 1& 3& 3& 9& 5& 4& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.49& 0.24& 0.41& 0.26& 0.12& 0.03& 0.26& 0.06& 0.19& 0.38& 0.02& 0.07& 0.2& 0.2& 0.32& 0.13& 0.86\\ \cline{2-20}
& wriggle& 0.2& 0.65& 0.19& 0.42& 0.37& 0.22& 0.56& 0.64& 0.26& 0.79& 0.97& 0.23& 0.52& 0.99& 0.78& 0.15& 0.58& 0.55\\ \cline{2-20}
& depthMin& 2& 4& 3& 2& 5& 5& 4& 3& 5& 4& 4& 2& 4& 2& 1& 4& 3& 1\\ \cline{2-20}
& depthMax& 10& 16& 7& 19& 11& 14& 16& 12& 12& 19& 17& 12& 13& 15& 13& 3& 17& 15\\ \cline{2-20}
& wherePrune& False& True& False& False& False& False& False& False& True& True& False& False& True& False& True& False& False& False\\ \cline{2-20}
& treePrune& True& True& True& True& False& False& False& False& False& True& True& False& False& True& False& False& True& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.01& 0.13& 0.01& 0.01& 0.06& 0.34& 0.01& 0.15& 0.39& 0.01& 0.05& 0.06& 0.01& 0.01& 0.18& 0.06& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.9& 0.01& 0.01& 0.45& 0.14& 0.52& 0.57& 0.76& 1& 0.68& 0.01& 0.33& 0.01& 0.73& 0.04& 0.01\\ \cline{2-20}
& min\_samples\_split& 2& 17& 20& 7& 18& 9& 11& 15& 16& 12& 11& 2& 6& 3& 13& 19& 13& 10\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 1& 9& 2& 19& 14& 6& 15& 4& 17& 19& 9& 12& 5& 4& 7& 13\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.09& 0.01& 0.01& 0.01& 0.36& 0.49& 0.08& 0.01& 0.01& 0.01& 0.05& 0.01& 0.01& 0.01& 0.2& 0.15& 0.01\\ \cline{2-20}
& max\_feature& None& 0.01& 0.63& 0.01& 1& 0.19& 0.17& 0.01& 0.01& 0.95& 0.01& 0.65& 0.54& 0.01& 0.01& 0.45& 0.63& 0.2\\ \cline{2-20}
& max\_leaf\_nodes& None& 31& 43& 28& 29& 11& 48& 17& 25& 13& 25& 10& 31& 33& 47& 44& 14& 23\\ \cline{2-20}
& min\_samples\_split& 2& 2& 7& 13& 1& 9& 13& 1& 13& 6& 10& 4& 12& 19& 16& 17& 3& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 17& 18& 2& 20& 2& 18& 9& 6& 7& 11& 17& 19& 8& 17& 3& 13& 9\\ \cline{2-20}
& n\_estimators& 100& 76& 64& 62& 141& 91& 67& 57& 104& 70& 67& 56& 59& 97& 81& 140& 85& 92\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of pd}
\end{figure*}

%%%%parameters for prec %%%%%%
\begin{figure*}[!ht]

\renewcommand{\baselinestretch}{0.8}
\resizebox{\textwidth}{!}{
\scriptsize
\centering
  \begin{tabular}{|c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |c |}
    \hline
  \begin{tabular}[c]{@{}c@{}}Learner \\ Name\end{tabular}&Parameters  & Default &antV0&antV1&antV2&camelV0&camelV1&ivyV0&jeditV0&jeditV1&jeditV2&log4jV0&luceneV0&poiV0&poiV1&synapseV0&velocityV0&xercesV0&xercesV1\\ 
 \hline
\multirow{8}{*}{\begin{tabular}[c]{@{}c@{}}Where\\based\\ Learner\end{tabular}}
& threshold& 0.5& 0.53& 0.48& 0.41& 0.35& 0.88& 1& 1& 0.9& 0.96& 0.57& 1& 1& 0.56& 0.57& 0.8& 0.26& 0.65\\ \cline{2-20}
& infoPrune& 0.33& 0.68& 0.74& 0.31& 0.45& 0.78& 0.31& 0.53& 0.85& 0.04& 0.73& 0.54& 0.15& 1& 0.98& 0.23& 0.9& 0.19\\ \cline{2-20}
& min\_sample\_size& 4& 3& 6& 5& 2& 1& 5& 7& 1& 7& 5& 2& 8& 1& 1& 1& 2& 2\\ \cline{2-20}
& min\_Size& 0.5& 0.07& 0.23& 0.2& 0.21& 0.25& 0.54& 0.18& 0.36& 0.28& 0.51& 1.0& 0.33& 0.5& 0.84& 0.83& 0.04& 0.21\\ \cline{2-20}
& wriggle& 0.2& 0.91& 0.77& 0.58& 0.85& 0.17& 0.66& 0.33& 0.88& 0.13& 0.72& 0.18& 0.07& 0.43& 0.63& 0.74& 0.18& 0.75\\ \cline{2-20}
& depthMin& 2& 4& 2& 5& 2& 4& 2& 2& 2& 4& 2& 3& 4& 1& 5& 1& 2& 1\\ \cline{2-20}
& depthMax& 10& 10& 14& 6& 13& 7& 16& 15& 14& 13& 19& 16& 9& 16& 14& 11& 13& 15\\ \cline{2-20}
& wherePrune& False& True& False& True& True& True& True& True& True& True& True& True& True& True& True& False& True& False\\ \cline{2-20}
& treePrune& True& True& True& True& True& True& True& False& False& False& True& False& True& True& False& False& False& False\\ \cline{2-20}
\hline
\multirow{4}{*}{CART}
& threshold& 0.5& 0.76& 0.99& 0.86& 0.48& 1& 1& 1& 0.71& 0.62& 0.65& 1& 0.95& 0.64& 0.5& 1& 0.99& 1\\ \cline{2-20}
& max\_feature& None& 0.09& 0.13& 0.05& 0.01& 0.01& 0.47& 0.01& 0.1& 0.63& 0.62& 0.44& 0.27& 0.28& 0.04& 0.75& 0.96& 0.21\\ \cline{2-20}
& min\_samples\_split& 2& 4& 19& 9& 9& 17& 14& 14& 16& 14& 12& 17& 3& 10& 12& 20& 13& 6\\ \cline{2-20}
& min\_samples\_leaf& 1& 15& 17& 8& 7& 1& 20& 1& 9& 12& 15& 10& 13& 7& 10& 4& 7& 20\\ \cline{2-20}
\hline
\multirow{6}{*}{\begin{tabular}[c]{@{}c@{}}Random \\ Forests\end{tabular}} 
& threshold& 0.5& 0.92& 0.99& 0.71& 0.7& 1& 0.82& 1& 1& 1& 0.96& 0.73& 1& 0.76& 0.33& 1& 1& 0.98\\ \cline{2-20}
& max\_feature& None& 0.23& 0.13& 0.46& 0.69& 0.37& 0.56& 0.71& 0.01& 1& 0.01& 0.85& 0.48& 0.34& 0.02& 0.01& 0.08& 0.62\\ \cline{2-20}
& max\_leaf\_nodes& None& 12& 49& 23& 39& 10& 17& 20& 10& 10& 44& 37& 18& 35& 11& 31& 35& 28\\ \cline{2-20}
& min\_samples\_split& 2& 18& 8& 14& 1& 11& 3& 2& 1& 4& 14& 2& 1& 13& 8& 18& 2& 13\\ \cline{2-20}
& min\_samples\_leaf& 1& 11& 5& 11& 3& 2& 4& 20& 2& 2& 10& 3& 7& 7& 15& 6& 2& 9\\ \cline{2-20}
& n\_estimators& 100& 130& 146& 66& 96& 50& 50& 136& 84& 83& 129& 51& 150& 99& 58& 88& 85& 61\\ \cline{2-20}
\hline  \end{tabular}
}
  \caption{Parameters tuned on different models over the objective of prec}
\end{figure*}

%%%%parameters for F %%%%%%
\begin{figure*}[!ht]
